Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)

### 2022-06-27 Manual.Rmd
updated manual outputs and readme

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)"
output: github_document
---

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)"
output: 
  github_document: default
  html_document: default
---
